Multivariate Skew-Normal Mixture Model for Infant Development Clustering

### 2019-05-29 poster/poster.tex
poster

\begin{table}[]
\caption{\label{tab:unnamed-chunk-4}Estimated effects of sex and race on odds of cluster membership relative to the reference cluster.}
\centering
\begin{tabular}{lll}
\hline
Variable & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Class 2\\ $\hat{\text{OR}}$ (95\% CrI)\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Class 3\\ $\hat{\text{OR}}$ (95\% CrI)\end{tabular}} \\ \hline
Intercept & 1.28 (1.01, 1.73) & 1.16 (0.87, 1.71) \\
Sex (Female) & 0.69 (0.40, 0.96) & 0.77 (0.48, 1.05) \\
Race (White) & 0.90 (0.57, 1.32) & 0.83 (0.59, 0.29) \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[]
\caption{\label{tab:unnamed-chunk-4}Estimated effects of sex and race on odds of cluster membership relative to the reference cluster.}
\centering
\begin{tabular}{lll}
\hline
Variable & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Class 2\\ $\hat{\text{OR}}$ (95\% CrI)\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Class 3\\ $\hat{\text{OR}}$ (95\% CrI)\end{tabular}} \\ \hline
Intercept & 1.28 (1.01, 1.73) & 1.16 (0.87, 1.71) \\
Sex (Female) & 0.69 (0.40, 0.96) & 0.77 (0.48, 1.05) \\
Race (White) & 0.90 (0.57, 1.32) & 0.83 (0.59, 1.29) \\ \hline
\end{tabular}
\end{table}
